---
name: Avishka &nbsp;
surname: Perera
position: "Data Scientist"
address: "Harrow, London"
phone: +44 07804542806
profilepic: avi.png
www: a-vip.github.io
email: "aviperera@gmail.com"
twitter: 
github: a-vip
linkedin: avi-perera
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "Avishka is a freelance Web Developer and a research enthusiast involved in Digital Distribution & Web Analytics. His areas of expertise include designing and developing websites, data analysis, project management, and research understanding. &nbsp; "
output: vitae::twentyseconds
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

Determined, self-motivated and trustworthy individual with excellent analytical abilities. I am organized and punctual and able to complete
tasks quickly and efficiently as well as being flexible and quick to adapt to all kinds of situations. Able to work under pressure
and I am always willing to develop and learn new skills. Greatly value analytical and different problem-solving skills.
Above all, I possess the ability to think on my feet, be creative, make connections between different topics and persevere until
I crack those difficult problems.



# Key Skills & Attributes

 * Advanced knowledge of computers with numerous IT skills.
 * Varying coding ability including Python, R, SQL, HTML and CSS.
 * Website development and industry knowledge in digital marketing.
 * Knows how to prepare, process, analyze, and share data for action.
 * Retrieving and evaluating data in spreadsheets and pivot tables.
 * Creating analysis reports or dashboards using RStudio and Tableau.
 * Able to solve complex problems and understand logical arguments.
 * An extraordinary eye for colour, contrast, and ratio.
 * Mathematical competence in areas of accountancy and IT.
 * Mathematical modelling for medical applications including clinical trials, statistics, physics, hypothesis testing, and many more.


# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Google Scholarship Program", "2021-2022","Google/Coursera", "London, England",
  "Mathematics for Machine Learning", "2021-2022", "Imperial College London", "London, England",
  "BSc Mathematics", "2018-2022", "The Open University", "London, England",
  "Informal Studies", "2008-2012", "Hatch End High School", "London, England"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Certifications & Licenses

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  2021, "Data Analytics", "Awarded from Google",
  2021, "Project Management", "Awarded from Google",
  2021, "IT Automation", "Awarded from Google",
  2020, "Data Science", "Awarded from IBM",
  2020, "Machine Learning", "Awarded from IBM"
) %>% 
  brief_entries(
    glue::glue("Certificate in {Type}"),
    Year, 
    Desc
  )
```

# Employment History

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Web Developer", "2021-2022", "Tame Digital", "London, England",
  "Web Developer", "2020-2022", "Upwork/Fiverr", "London, England",
  "Conferences & Events", "2019-2020", "Hilton Wembley", "London, England",
  "VIP Events Staff", "2018-2019", "Hospitality Company", "London, England",
  "Data Scientist", "2017-2018", "World News Inc", "London, England",
  "Teaching Assistant", "2010-2013","FISTS Taekwondo", "London, England"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Additional Info & Achievments

 * Competent in tools and platforms including spreadsheets, SQL, Tableau.
 * Made this resume using R programming & markdown code on RStudio.
 * Looking to develop analytical skills to achieve a career in data science.



•References: Available on request
 